%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{ifthen}
\usepackage{multicol}

\usepackage{xparse}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \ifthenelse{\equal{#2}{}}{
    \item\small{
      \textbf{#1}
    }
  }{
    \item\small{
      \textbf{#1}{: #2 \vspace{-2pt}}
    }
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{
  \resumeItem{#1}{#2}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://lukebechtel.com/}{\Large Luke Bechtel}} & \href{mailto:luke@lukebechtel.com}{luke@lukebechtel.com}\\
  \href{http://www.lukebechtel.com/}{http://www.lukebechtel.com} & Github: \href{https://github.com/Marviel}{@Marviel} \\
  & Twitter: \href{https://twitter.com/linkbechtel}{@linkbechtel} \\
\end{tabular*}

%-----------PROFESSIONAL SUMMARY-----------------
\section{Professional Summary}
AI/ML Technical Founder with 12+ years building production systems, specializing in LLM orchestration, agentic AI workflows, and full-stack development. Currently bootstrapping EdTech startup while running profitable AI consulting practice. Proven track record leading technical teams from prototype to production-scale systems.

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  
  \resumeSubheading
  {Reasonote}{Remote}
  {Founder / CEO}{May 2024 - Present}
  \resumeItemListStart
    \resumeItem{AI-Powered EdTech Platform}
      {Bootstrapped personalized learning platform achieving 1000+ users and 4000+ generated lessons. Built sophisticated multi-LLM orchestration pipeline integrating OpenAI, Anthropic, Gemini, and Llama models with custom infrastructure layer.}
    \resumeItem{Technical Leadership}
      {Single-handedly architected full-stack platform using Next.js, Postgres, PGVector, and Vercel AI SDK. Implemented agentic content creation, real-time streaming, and LLM-driven grading pipeline with automated assessment and feedback generation.}
  \resumeItemListEnd

  \resumeSubheading
  {Positive Sum Products}{Remote}
  {Founder / CEO}{May 2024 - Present}
  \resumeItemListStart
    \resumeItem{AI/ML Consulting \& Development}
      {Founded specialized consulting firm delivering custom AI/ML solutions while bootstrapping Reasonote. Built content extraction pipelines improving processing efficiency by 90\% and accuracy by 80\%.}
    \resumeItem{Agentic AI Systems}
      {Pioneered autonomous code generation and review systems using collaborative LLM agents. Developed intelligent suggestion systems for email analysis and automated workflow optimization.}
  \resumeItemListEnd

  \resumeSubheading
  {Regscale}{Remote}
  {Principal AI/ML Engineer}{April 2023 - June 2024}
  \resumeItemListStart
    \resumeItem{Document Intelligence Tools}
      {Built document corpus extraction and evaluation tools for automated Q\&A form generation. Sole designer and developer of core processing pipeline.}
    \resumeItem{Cross-Platform AI Libraries}
      {Led development of TypeScript library for LLM orchestration, evaluation, and management. Built custom providers for OpenAI, Anthropic, and Azure OpenAI with plugin architecture supporting multiple platforms.}
  \resumeItemListEnd

  \resumeSubheading
  {Revaly}{Remote}
  {Director of Engineering}{Oct 2020 - April 2023}
  \resumeItemListStart
    \resumeItem{Real-time 3D Collaboration Platform}
      {Led team of 6 building collaborative 3D design review webapp. Architected real-time multiplayer system using GraphQL, Postgres, and WebSockets supporting cross-platform usage.}
    \resumeItem{Technical Architecture \& Team Leadership}
      {Designed microservice architecture on Kubernetes with complete DevOps pipeline. Managed hiring, product development, and stakeholder relationships from prototype to production.}
  \resumeItemListEnd

  \resumeSubheading
  {Earlier Experience}{Various}
  {Software Engineer \& Research}{2013 - 2020}
  \resumeItemListStart
    \resumeItem{Collider (Cofounder)}{Led scientific computing for next-gen 3D printing, including firmware, geometry processing pipelines, and WebGL interfaces. Managed end-to-end product development generating significant revenue.}
    \resumeItem{Oak Ridge National Laboratory}{Developed ground control systems for remote vehicles and radiation visualization interfaces. Managed sensitive data applications.}
    \resumeItem{University Research}{Contributed to FPGA-accelerated neural network research and published IEEE paper on neuromorphic architecture extensions.}
  \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------------
\section{Technical Skills}
 \resumeSubHeadingListStart
     \resumeSubItem{AI/ML}{LLM Orchestration, Agentic AI, OpenAI/Anthropic APIs, Embeddings, RAG, Neural Networks, PyTorch}
     \resumeSubItem{Languages}{Python, TypeScript, JavaScript, Kotlin, C\#, C++, SQL, GLSL}
     \resumeSubItem{Full-Stack}{React, Next.js, Node.js, GraphQL, Three.js, WebGL, Django, Rails}
     \resumeSubItem{Infrastructure}{Docker, Kubernetes, Postgres, AWS, Azure, Vercel, Git, CI/CD}
     \resumeSubItem{Specialized}{Real-time Systems, Microservices, Vector Databases, 3D Graphics, WebRTC}
 \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Remote}
      {Masters in Computer Science, Machine Learning (Incomplete)}{Aug 2020 - Aug 2021}
    \resumeSubheading
      {University of Tennessee}{Knoxville, TN}
      {Bachelor of Science in Computer Science}{Aug 2011 - May 2020}
  \resumeSubHeadingListEnd

%-----------NOTABLE PROJECTS-----------------
\section{Notable Projects \& Contributions}
  \resumeSubHeadingListStart
    \resumeSubItem{Open Source}{Early contributor to Trimesh (primary Python 3D mesh library), Supabase, and other projects used by PyTorch3D and Blender}
    \resumeSubItem{AI Research}{Interrogato (GPT-3 academic paper research tool), Lab Grad (TypeScript PyTorch reimplementation)}
    \resumeSubItem{Publications}{Co-author: "Extensions and Enhancements for the DANNA Neuromorphic Architecture" (IEEE)}
  \resumeSubHeadingListEnd

\end{document} 